Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2018-12-21 paper/ms.tex
Add cluster offset to paper
Add captions to figures

\correspondingauthor{Angus Beane}
\email{abeane@sas.upenn.edu}

@@

\begin{figure*}
\plotone{fig/cartoon.pdf}
\caption{Caption.}
\label{fig:cartoon}
\end{figure*}

@@

\begin{figure*}
\plotone{fig/one_orbit.pdf}
\caption{Caption.}
\label{fig:one_orbit_wrong_ref}
\end{figure*}

@@

>>>>

% \correspondingauthor{Angus Beane}
\email{abeane@sas.upenn.edu}

@@

\begin{figure*}
\plotone{fig/cartoon.pdf}
\caption{Cartoon showing the effect an incorrect midplane can have on orbit
integrations and as an extension on action computations. The x-axis shows the
orbital phase and the y-axis the vertical height. The top gray curve depicts a
hypothetical true orbit oscillating about the true midplane, the horizontal
solid gray line. Consider an immortal observer who erroneously assumes the
midplane is located at the horizontal dashed line. Suppose this immortal
observer measures the orbit at the blue and pink points. If the immortal
observer were to perform orbit integrations at each observation, they would
assume the blue and pink curves for the respective orbits. In this way, an
incorrect midplane will induce phase-dependence in the {\em observed}
actions.}
\label{fig:cartoon}
\end{figure*}

@@

\begin{figure*}
\plotone{fig/one_orbit.pdf}
\caption{The artificial phase-dependence in the observed actions induced by an
error in the Galactocentric coordinate system. We consider here an orbit with
initial position $(8,0,0)\,\kpc$ and initial velocity $(0,-190,50)\,\kms$.
This corresponds to an orbit with actions $(J_r, L_z, J_z) = (32.5, -1520,
23.0)\,\actunit$ and $z_{\text{max}}=854\,\pc$. Considering the first $\Gyr$
of this orbit, we assume an immortal observer }
\label{fig:one_orbit_wrong_ref}
\end{figure*}

@@

\begin{figure}
\plotone{fig/cluster_offset.pdf}
\caption{Caption.}
\label{fig:cluster_offset}
\end{figure}

In Figure~\ref{fig:cluster_offset}, we show the $z$ offset necessary to induce
the action space dispersion computed from Equation~\ref{eq:action_disp}, using
the \texttt{gala} computed mass enclosed within a radius of $8.2\,\kpc$ ($\sim
10^{11}\,[\,M_{\odot}\,]$).
